My Cool Title

### 2019-04-30 paper.tex
Adde dguided section

To evaluate the effectiveness of our POMDP controller and guidance system, we designed a set of experiments that can measure its performance in driving a user towards a target object within the environment. 
We also conducted an additional set of experiments with an alternative guidance system to act as a baseline measurement to compare our results to and provide additional context. 
This alternative `guidance' system does not actually provide any guidance instructions to the user, instead it provides the user with the raw observation output from the object classifier and makes use of the user's intuition and prior environment knowledge to generate actions. 
The goal of both the guided and unguided experiment cases were to find an object within a static environment. 
Details on the design of these experiments are given in the next sections.

@@

For this experiment, a mobile camera and object detector acts as the participant's eyes and informs them what the objects within the camera's view and it is then up to the participant to exploit their prior knowledge of the given environment in order to manipulate the camera to point towards the target object. 
The object detector was implemented in an Android app that uses the object classifier and Android's Text-to-Speech engine to read out any objects that it detected. 
The app only reads out the objects when the participant requested it to by tapping on the screen. 
When the target object comes within the camera's view and is correctly classified by the object detector, the device vibrated to inform the participant.

@@

>>>>

To evaluate the effectiveness of our POMDP controller and guidance system, we designed a set of experiments that can measure its performance in driving a user towards a target object within the environment. 
We also conducted an additional set of experiments with an alternative guidance system to act as a baseline measurement to compare our results to and provide additional context. 
This alternative `guidance' system does not actually provide any guidance instructions to the user, instead it provides the user with the raw observation output from the object classifier and makes use of the user's intuition and prior environment knowledge to generate actions. 
The goal of both the guided and unguided experiment cases were to find an object within a static environment.

We recruited 10 sighted participants that were blindfolded for the experiments, as well as 2 legally blind participants, where 1 was blind from birth and the other suffers from late onset blindness\todo{Give participant stats}.
Details on the design of these experiments are given in the next sections.

@@

For this experiment, a mobile camera and object detector acts as the participant's eyes and informs them what the objects within the camera's view and it is then up to the participant to exploit their prior knowledge of the given environment in order to manipulate the camera to point towards the target object. 
This process is modelled by the schematic in Fig. MEME\todo{put in figure without controller} where the human, \emph{H}, acts as both the actuator and controller.
The object detector was implemented in an Android app that uses the object classifier and Android's Text-to-Speech engine to read out any objects that it detected. 
The app only reads out the objects when the participant requested it to by tapping on the screen. 
When the target object comes within the camera's view and is correctly classified by the object detector, the device vibrated to inform the participant.

@@

In this experiment, we evaluate the performance of the guidance system in the object search task, where the perception and control tasks are performed by the guidance system and mobile device and the participant acts as the actuator, interpreting control signals and outputting actuation forces on the camera sensor. 
This is modelled by the schematic in Fig.~\ref{fig:sys-diagram}.

The participants were not told what the targets objects were in this experiment to eliminate the possibility of them ignoring the guidance instructions in order to try and find the target object themselves.
An experiment run was therefore initiated when the experiment staff selected the target and was terminated when the target object was found or the time limit was exceeded.
We set a time limit of 45 seconds in this experiment as well.
Each participant repeated this experiment 8 times, once for each object within the experiment's object set.
